Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-19 doc/report/msc-report.tex
report: tagged FINAL
report: tagged PRINT.0

\begin{adjustwidth}[]{20mm}{-40mm}
    {\huge \textbf{Zohmg---a large scale data store for \\
    aggregated time-series-based data. [DRAFT]}}

@@

\noindent Zohmg---a large scale data store for aggregated time-series-based
data.

>>>>

\begin{adjustwidth}[]{20mm}{-40mm}
    {\huge \textbf{Zohmg---A Large Scale Data Store for \\
    Aggregated Time-series-based Data}}

@@

\noindent Zohmg---A Large Scale Data Store for Aggregated Time-series-based
Data
